Merging Datasets Through Deep learning

### 2018-09-03 paper2018/introduction2.tex
minor fixes

Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{John Adams} and \textit{Adams, John}.  Similarly, ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  For matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  In other words, `hard negatives' dominate the space, and are the norm.  Our approach to the problem of triplet mining for this problem was to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that suitable for use in joins than semi-hard triplet mining.

We also investigated the effect of manipulating multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the objective function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature. 
%
%\begin{table}[!htb]
%    \caption{Example of a merge problem}
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table A}
%        \begin{tabular}{|l|l|}
%          \hline
%           Dept & Name \\
%           \hline
%           1    & Douglas Adams \\
%           2    & John Adams \\
%           3  & Douglas Bard \\
%           \hline
%        \end{tabular}
%    \end{subtable}%
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table B}
%        \begin{tabular}{|l|l|}
%          \hline
%           Name & Salary \\
%           \hline
%           Douglas Noel Adams & 2000 \\
%           Adams, John & 3000 \\
%           John Smith & 3000 \\
%           \hline
%        \end{tabular}
%    \end{subtable}
%    \label{table-example}
% \end{table}

>>>>

Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity.  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{D. Adams} and \textit{Adams, Douglas}.  Similarly, ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  In other words, `hard negatives' dominate the space, and are the norm.  Our approach to the problem of triplet mining was therefore to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that suitable for use in joins than semi-hard triplet mining.

We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature. 
%
%\begin{table}[!htb]
%    \caption{Example of a merge problem}
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table A}
%        \begin{tabular}{|l|l|}
%          \hline
%           Dept & Name \\
%           \hline
%           1    & Douglas Adams \\
%           2    & John Adams \\
%           3  & Douglas Bard \\
%           \hline
%        \end{tabular}
%    \end{subtable}%
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table B}
%        \begin{tabular}{|l|l|}
%          \hline
%           Name & Salary \\
%           \hline
%           Douglas Noel Adams & 2000 \\
%           Adams, John & 3000 \\
%           John Smith & 3000 \\
%           \hline
%        \end{tabular}
%    \end{subtable}
%    \label{table-example}
% \end{table}

### 2018-09-03 paper2018/main.tex
minor fixes

\maketitle
\begin{abstract}
Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to performing merges
based on deep learning models.  Our approach depends on (a) creating
a deep learning model that maps surface forms of an entity into a
set of vectors such that alternate forms for the same entity are
closest in vector space, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we had to adapt techniques from
metric learning, due to the requirements of joins; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models for datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We found developed models that 
allow for joins with precision@1 of .73-.81 and
recall of .72-.81.  We make the models available to the community
for aligning people or companies across multiple datasets.  
\end{abstract}

>>>>

\maketitle
\begin{abstract}
Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to performing merges
based on deep learning models.  Our approach depends on (a) creating
a deep learning model that maps surface forms of an entity into a
set of vectors such that alternate forms for the same entity are
closest in vector space, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we had to adapt techniques from
metric learning due to the requirements of joins; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models for datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We found developed models that 
allow for joins with precision@1 of .73-.81 and
recall of .72-.81.  We make the models available to the community
for aligning people or companies across multiple datasets.  
\end{abstract}
